\documentclass[12pt]{article}
\usepackage{amsmath}
\begin{document}
\title{Photometry and images from smart telescopes}

\section{Introduction}

Smart telescopes, such as the SeeStar S50 (etc...) are very popular and eliminate
most of the barriers to entry into astrophotography. For a relatively modest price
a smart "telescope" is the optical componenets of a telescope, a one-shot-color
CMOS sensor, a housing, and a basic trtipod. The device takes regular, short
exposures, e.g. 10 seconds for the SeeStar S50, plate solves each exposure and
builds a stacked color image on the fly. Image taking continues until the user
stops it. The user has the option of saving only the stacked color image or the
stacked image and also of the subframes that went into the stack.

While manufacturers of these devices have focused on their use for
astrophotography, the CMOS sensors in them are adequate for performing aperture
photometry on the stars in the image. The devices typically have a wide field
of view so as to maximize the visual impact of the images they take. That implies
a fairly large pixel scale of 1-2 arcsec/pixel with a stellar full-width at half maximum (FWHM) of 3-5 pixels.

The combination of under-resolved stars and a Bayer array on the image sensor is a challenge. The traditional approach of separating the one-shot color image into
three separate lower-resolutions images, one for each each of the three color channels, will lead to severely under-resolved stars. In this paper we present an alternative method based on applying masks to the image to select one color at
a time.

In Section \ref{sec:method} we describe our methods for performing photometry on
both individual subframes and stacked images. Section \ref{sec:results} presents the application of these methods to a few variable stars and smart telescopes. Finally, Section \ref{sec:conclusions}
\end{document}
